Review of Assigned Readings

### 2018-01-05 paper/paper.tex
adjusted and corrected chapter 1

\textcite[p.~388]{malkiel1970efficient} introduced the Efficient Market Hypothesis (EMH), where they claim that under certain market conditions actual prices include all information. This hypothesis is broadly accepted in the financial world. The digitalisation leads to an increased network effect, where information can be shared over the globe. Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors. The large fluctuation of the Bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on Bitcoin and Twitter. \textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using Twitter tweets which contain the buzzword bullishness can indeed be used as a sentiment indicator for stock prices. As modern economy becomes more digitized, crypotocurrencies as a financial asset draws more attention, our paper seeks to shed some light on whether the tweets can be used to predict Bitcoin prices.

@@

As existing research focus mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of Bitcoin and the frequency of Bitcoin topics on Twitter. The goal should be reached by answering the following research question: \\
To what extent does the amount of Twitter tweets about Bitcoin correlate with the price movement of Bitcoin?

\subsection{Methodology}
\label{sec:Methodology}
To answer the above mentioned research question a scientific approach has been applied. The paper consists out of three parts. The first part contains an introduction into the topic by pointing out the relevance of the topic, the research question, methodology and the scope. This is conducted in chapter \ref{sec:intro}. The second part is characterized as the theory part. The theory aims to provide the reader with the necessary background information by introducing relevant Bitcoin and Twitter information in context of the paper. The conducted research is based on forward research and using relevant sources. Furthermore, it contains a short introduction into the Vector Autoregression (VAR) approach and its constrains in context with the paper. This is conducted in chapters \ref{sec:Background} and \ref{sec:EconometricModellingandResults}. The third part contains the discussion of the results and a conclusion. The conclusion is based on the theory and our mathematical computation. The computation is based on a data set, which was gathered by coded python scripts for the time period December 20th - 27th. Since the results are based on the observation of a short period, they have to be interpreted carefully. The data set consists of two data sources with the following characteristics: (1) Twitter tweets which contain the buzzword "Bitcoin" and (2) those containing historical Bitcoin prices. The two sources has been aggregated with another python script. The output of aggregation was further processed with Stata to conduct the VAR on a daily basis. The third part of the paper is discussed in the chapters \ref{sec:EconometricModellingandResults} and \ref{sec:Conclustion}.

\subsection{Scope}
\label{sec:Scope}
The paper's focus lies on the scientific discussion of empirical test results. The research question has consciously been narrowed down, as the focus of the course Software Engineering for Economists is the application of different tools, the documentation and reproducibility of the results. As already mentioned above, the results have to be interpreted carefully because of the limited observation period of seven days. However, the results provide a first impression and can be further be developed. The approach and technical issues (like code scripts etc.) are not addressed, for purposes we shall address in a separate documentation paper.

@@

Twitter was founded in 2006 and gained rapidly worldwide popularity and reached 330 million active users in the third quarter of 2017  (\cite[]{twitterinc2018}; \cite[]{Statista2018b}). As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests due to its special characteristics. In comparison to other social networks, twitter limits its posts (tweets) to relatively short messages of 140 characters. Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos. Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(\cite{Schmidt2018socialmedia})\\

@@

In relation to Bitcoin, researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies \textcite[p.~7]{stenqvist2017predicting} , by either using a \textit{polarity classification} {-} classifying the language in tweets as either positive or negative (see \cite{colianni2015algorithmic}) {-} or a \textit{lexicon based approach} {-} attributes predefined words to specific sentiment classifications (see \cite{stenqvist2017predicting}). Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further. Based on analysis of the influence of twitter bullishness on the stock market by \textcite{mao2015quantifying}, this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\

@@

This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term. The second equation is directly relevant to our research question, as it allows to look into the correlation between the present bitcoin price and the past tweet count.\\

>>>>

\textcite[p.~388]{malkiel1970efficient} introduced the Efficient Market Hypothesis (EMH), where they claim that under certain market conditions actual prices include all information. This hypothesis is broadly accepted in the financial world. The digitalisation leads to an increased network effect, where information can be shared over the globe. Based on \citeauthor{mao2015quantifying} (\citeyear[][p.~3]{mao2015quantifying}, as cited in \cite[][pp.~175--195]{shiller2015irrational}; \cite[][pp.~279]{kahneman2013prospect}) the EMH fails to address the behavioural and emotional role of investors. The large fluctuation of the Bitcoin prices in the last year (mostly increasing) and the fact that Twitter has become a very popular social network, where people interact, led to different research in the field of sentimental analysis with the focus on Bitcoin and Twitter. \textcite[p.~18]{mao2015quantifying}, claim that sentiment analysis using Twitter tweets which contain the buzzword "bullishness" can indeed be used as a sentiment indicator for stock prices. As the modern economy becomes more digitised, crypotocurrencies, as a financial asset, draw more attention. This paper seeks to shed light on whether the tweets can be used to predict Bitcoin prices.

@@

As existing research focuses mostly on the sentimental analyses of tweet content, this paper aims to examine existence of a correlation between the price development of Bitcoin and the frequency of Bitcoin topics on Twitter. The goal should be reached by answering the following research question: \\
To what extent does the number of tweets about Bitcoin correlate with the price movement of Bitcoin?

\subsection{Methodology}
\label{sec:Methodology}
To answer the above mentioned research question, a scientific approach has been applied. The paper consists out of three parts. First, the relevance of the topic is pointed out by the introduction , the research question, methodology and the scope (see chapter \ref{sec:intro}). Secondly, the related theory has been analysed to provide the reader with the necessary background information by briefly introducing both Bitcoin and Twitter in context of price prediction and behavioural finance. The covered research is based on forward research in regard to the stock market and cryptocurrencies with a special focus on sentiment analysis and Bitcoin \ref{sec:Background}. Further on,  Vector Autoregression (VAR) approach is introduced and its constrains in context of the paper are being outlined (see chapter \ref{sec:EconometricModellingandResults}). The third part contains the discussion of the results. The computation is based on a data set, which was gathered by Python scripts for the time period December 20th - 27th. Since the results are based on the observation of a short period, they have to be interpreted carefully. The data set consists of two data sources with the following characteristics: (1) Twitter tweets which contain the buzzword "Bitcoin" and (2) those containing historical Bitcoin prices. The two sources have been aggregated by using Python. The output of the aggregation was further processed with STATA. The third part of the paper is discussed in the chapter \ref{sec:EconometricModellingandResults} followed by a brief conclusion in chapter \ref{sec:Conclustion}.

\subsection{Scope}
\label{sec:Scope}
The paper's focus lies on the scientific discussion of empirical test results. The research question has consciously been narrowed,in order to build up on a existing methodology for sentiment analysis in the stock market while simultaneously extending the research scope in the area of behavioural finance and sentiment analysis for cryptocurrencies. The short time frame of our project further limited the period of data collection which has a direct impact on the reliability of our results.\\
Further on, this paper should act as a blueprint for further research in the area of Twitter sentiment analysis for cryptocurrencies. Therefore, the accompanying project documentation can be used as a guideline for further research.

@@

Twitter was founded in 2006 and gained rapidly worldwide popularity and reached 330 million active users in the third quarter of 2017  (\cite[]{twitterinc2018}; \cite[]{Statista2018b}). As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests due to its special characteristics. In comparison to other social networks, Twitter limits its posts (tweets) to relatively short messages of 140 characters. Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos. Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(\cite{Schmidt2018socialmedia})\\

@@

In relation to Bitcoin, researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies \textcite[p.~7]{stenqvist2017predicting} , by either using a \textit{polarity classification} {-} classifying the language in tweets as either positive or negative (see \cite{colianni2015algorithmic}) {-} or a \textit{lexicon based approach} {-} attributes predefined words to specific sentiment classifications (see \cite{stenqvist2017predicting}). Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further. Based on analysis of the influence of Twitter bullishness on the stock market by \textcite{mao2015quantifying}, this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\

@@

This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term. The second equation is directly relevant to our research question, as it allows to look into the correlation between the present Bitcoin price and the past tweet count.\\
